A Descriptive Analysis of How Psychology Journals Handle Post-Publication

### 2024-01-05 manuscript/manuscript_NHB.Rmd
Corrected # COPE code descriptions

# COPE membership status among prominent journals NOT accepting PPC
random_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
  summarise(count = n()) # total number journals accepting PPC

rand_copeY_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

rand_copeN_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
  summarise(count = n()) # number of non-COPE journals accepting PPC

>>>>

# COPE membership status among prominent journals NOT accepting PPC
random_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that do not accept PPC
  summarise(count = n()) # total number journals not accepting PPC

rand_copeY_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that do not accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

rand_copeN_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that do not accept PPC)
  summarise(count = n()) # number of non-COPE journals not accepting PPC
